#

---
title: "Adaptive Subgroup Selection in Sequential Trials"
author: "Tze Leung Lai, Philip W. Lavori, Olivia Liao, Ka Wai Tsang
and Balasubramanian Narasimhan"
date: '`r Sys.Date()`'
bibliography: assistant.bib
output:
  html_document:
  theme: cerulean
  toc: yes
  toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Adaptive Subgroup Selection in Sequential Trials}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo=F}
### get knitr just the way we like it

knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = FALSE
)
```

## Introduction

`ASSISTant` is an R package for **A**daptive **S**ubgroup
**S**election **I**n **S**equential **T**rials. This vignette
reproduces all the simulations in the original paper of Lai, Lavori
and Liao [-@Lai2014191].


```{r}
library(ASSISTant)
data(LLL.SETTINGS)
str(LLL.SETTINGS)
```

The `LLL.SETTINGS` list contains all the scenarios described in the
paper.

## Table 1 Results

### Scenario S0
```{r}
scenario <- LLL.SETTINGS$scenarios$S0
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S1
```{r}
scenario <- LLL.SETTINGS$scenarios$S1
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S2
```{r}
scenario <- LLL.SETTINGS$scenarios$S2
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S3
```{r}
scenario <- LLL.SETTINGS$scenarios$S3
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S4
```{r}
scenario <- LLL.SETTINGS$scenarios$S4
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S5
```{r}
scenario <- LLL.SETTINGS$scenarios$S5
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S6
```{r}
scenario <- LLL.SETTINGS$scenarios$S6
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S7
```{r}
scenario <- LLL.SETTINGS$scenarios$S7
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S8
```{r}
scenario <- LLL.SETTINGS$scenarios$S8
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S9
```{r}
scenario <- LLL.SETTINGS$scenarios$S9
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S10
```{r}
scenario <- LLL.SETTINGS$scenarios$S10
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table1,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

## Table 2 Results

### Scenario S0
```{r}
scenario <- LLL.SETTINGS$scenarios$S0
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S1
```{r}
scenario <- LLL.SETTINGS$scenarios$S1
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S2
```{r}
scenario <- LLL.SETTINGS$scenarios$S2
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S3
```{r}
scenario <- LLL.SETTINGS$scenarios$S3
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S4
```{r}
scenario <- LLL.SETTINGS$scenarios$S4
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S5
```{r}
scenario <- LLL.SETTINGS$scenarios$S5
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S6
```{r}
scenario <- LLL.SETTINGS$scenarios$S6
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S7
```{r}
scenario <- LLL.SETTINGS$scenarios$S7
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S8
```{r}
scenario <- LLL.SETTINGS$scenarios$S8
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S9
```{r}
scenario <- LLL.SETTINGS$scenarios$S9
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```

### Scenario S10
```{r}
scenario <- LLL.SETTINGS$scenarios$S10
designParameters <- list(prevalence = LLL.SETTINGS$prevalences$table2,
                       mean = scenario$mean,
                       sd = scenario$sd)
designA <- ASSISTDesign$new(trialParameters = LLL.SETTINGS$trialParameters,
                            designParameters = designParameters)
print(designA)
```

```{r}
result <- designA$explore(numberOfSimulations = 5000, showProgress = FALSE)
analysis <- designA$analyze(result)
print(designA$summary(analysis))
```




